Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-04 Final-Draft.Rmd
s

# 2. Data
```{r results = "hide", echo=FALSE, warning=FALSE, message = FALSE}

@@

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
day_initial<- as.Date("2020-03-14")
day_final<- as.Date("2020-03-21")
Finaldata<- Finaldata%>%
  filter(Day>=day_initial)%>%
  filter(Day<=day_final)

names(Finaldata)
```

@@

### 2.3a Demographic 
```{r, warning=FALSE, message= FALSE, echo=FALSE}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)

p1<- plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% White")

ggplotly(p1)

@@

ggplotly(p2)

@@

e
```

>>>>

# 2. Data
```{r}

@@

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
day_initial<- as.Date("03/14/2020")
day_final<- as.Date("03/21/2020")

Finaldata<- Finaldata%>%
  filter(Day>=day_initial)%>%
  filter(Day<=day_final)

View(Finaldata)
```

@@

### 2.3a Demographic

```{r}
Finaldata$hover <- with(Finaldata, paste(State, '<br>', "Positive Cases:", positive, "<br>","Positive Negative:", negative,"<br>",
                           "Total Cases:", totalTestResults,"<br>", "% White:", percent_white,"<br>",
                            "% Asian:", percent_asian, "<br>", "State Color:", StateColor))
# give state boundaries a white border
l <- list(color = toRGB("white"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

fig <- plot_geo(Finaldata, locationmode = 'USA-states')
fig <- fig %>% add_trace(
    z = ~ChinaVirusInterest, text = ~hover, locations = ~State,
    color = ~ChinaVirusInterest, colors = 'Purples'
  )
fig <- fig %>% colorbar(title = "Interest")
fig <- fig %>% layout(
    title = '2020 COVID-19 Cases, Demographics, & Politics by State<br>(Hover for breakdown)', geo=g
  )

fig
```

```{r, warning=FALSE, message= FALSE, echo=FALSE}
#Demographic: Identification 
Finaldata <- data.frame(Finaldata) %>% mutate(state = State)

plot_usmap(data = Finaldata, values = "percent_white", color = "white") + 
  scale_fill_continuous(name = "Percent White", label = scales::comma) + 
  theme(legend.position = "right")+ ggtitle("Percent of Residents that Identify as White") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_viridis_c(option = "plasma") + theme(plot.title = element_text(size=11))+ labs(fill = "% White")
p1

@@

@@

ggplotly(e)
```
